\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-02-24 doc/sw-cfhtls.tex

Since the inception of the first citizen science project, Galaxy Zoo, to
classify galaxy morphologies \citep{LintottEtal2008}, several astronomy
and non-astronomy projects have been launched by the Zooniverse leading
to many interesting project. For example, PlanetHunters
has discovered XXX transiting exoplanets \citep{SchwambEtal2012},
Supernova XXX add ref and XXX add ref

@@

@@

At galaxy-scales, we focus on two primary lens searches. The RingFinder
\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
of isolated and massive early-type galaxies. By subtracting the PSF-matched
$i$-band images from the $g$-band images, the algorithm looks for excess flux
in the bluer $g$-band. An object detector measures the properties of these
residual blue features, and candidates meeting length-width ratio and
tangential alignment criteria are then visually inspected to form the final
sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
photometrically-classified early type galaxies, or objects selected to have
red centers and blue outer parts, from the T06 CFHTLS data release catalogs. 
14370 were found to show detectable blue residuals, and 2524 were visually
inspected, having passed the automatic feature selection process. This led to
a sample of 42 good quality (\texttt{q\_flag} = 3) and 288 medium quality
(\texttt{q\_flag} = 2) lens candidates. In addition to this well defined
sample, \citet{Gavazzi2014} reported a further 71 serendipitously detected
lens candidates.  From this sample of ``RingFinder candidates,'' the SL2S team
found, during their follow-up campaign, 39 confirmed lenses (and 17 promising
candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
completeness analysis.

@@

On the other hand, the {\sc arcfinder} \citet{More2012} was used for
finding blue arc-like features in the complete \cfhtls data withouth any
pre-selection on the type of the lensing object. The search was carried
out in the g-band which is the most efficient wavelength to find typical
lensing galaxies. This sample, called the SARCS, has 55 promising and a
total of 127 lens candidates and consists of both galaxy and
groups/cluster scale lens candidates. Arc finding is better suited for
lensed images or arcs with larger image separations i.e. more massive
systems like groups and clusters. Thus, the SARCS sample has mostly
groups/cluster-scale lenses and a few galaxy-scale lenses.

@@

XXX refer Paper I ?

\subsection{Image Presentation}
\label{sec:data:impres}
{\it Preparation of data: divide survey into overlapping tiles.

Presentation of images. Uniform scales, to build intuition and avoid rescales
due to bright objects. Arcsinh stretch, to bring out low SB features. 
Approximately optimized, how? Examples of images.}

We carry out a blind search over the \cfhtls fields where we, mainly, use
the g-r-i color information to look for signs of lensing. We extract
contiguous cutouts of size 81.84\arcsec\ (440 pixels). The neighbouring
cutouts have an overlapping region of 10\arcsec (54 pixels). If a
possible lens candidate is too close to the edge of a cutout, this
overlap allows the inspector to get a clearer view of the same candidate
in a neighbouring cutout. We note that since the images are shown
randomly, a given inspector may not necessarily come across the
neighbouring cutout unless the inspector classifies a lot of images.
However, this is not a problem since we our user base is extremely large
and we get multiple classifications of the same image.

@@

We use the $L-\sigma$ relation from
\citep{Parker2007} to get the velocity dispersion as given in Eq.~\ref{magstar2}.

@@

\subsubsection{Groups-scale lenses}

@@

Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
Lens shear pa &  0 & 180 & 0 & 180  \\
Source ellipticity & 0.1 & 0.6 & & \\
Source PA & 0 & 180 & & \\
\hline
\end{tabular}
{ $\dagger$} -- corresponds to the factor used for Groups scale lenses. 
\end{center}
\end{table}

@@

We selected a sample of 450 duds for the Stage I classification in \sw
(see XXX) and a sample of XXX false positives for the Stage II
inspection (see XXX). The sample of false positives was selected from
the candidates which passed the Stage I of \sw. We note that this is the
first time, we have a systematically compiled sample of visually
inspected false positives by the \sw users and categorized by the
science team. Such a sample is tremendously helpful for training and
understanding performances of various lens finding algorithms (refer
james, sherry's paper ? XXX)
{\bf TBA data products; make the FP sample available}

\section{Results}
\label{sec:results}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection{\sw Lens Sample}
Here, we describe

\subsubsection{Selection of \sw lens candidates}
\label{sec:results:stage1}
The images inspected at stage II are assigned P values through the SWAP
built in the \sw system. Ideally, we would like to have all real lens
candidates to be assigned high P values. It is not known a priori what
value of P would give an optimal trade off between high completeness
and high purity.

Also, since this is the first lens search with \sw, we
would like to understand how the P correspond to the grades, typically,
assigned by lens experts.

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
\caption{ \label{fig:exp_pn} Comparison of the P(lens) with the expert
grades and number of classification for each subject.  }
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P.pdf}
\caption{ \label{fig:stackP} Total number of detections of the known
candidates, new candidates and the FPs shown relatively for binned
values of P.
}
\end{center}
\end{figure}

@@

{\bf \textcolor{red} {
CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
and P value comparison, what about the duplicate lenses near the borders
- stats on those?}}

{\it Describe the newly found lenses and explain for a few
cases why they were missed }

\begin{table}
\begin{center}
\caption{ \label{tab:stats} 
Statistics of detections in \sw }
\begin{tabular}{l l l l l l}
\hline
   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{3}{c}{Stage II} \\ 
      & KnCa  &  KnCo  & KnCa & KnCo & NeCa \\
\hline
\hline
Number  & 128 & 34 & 107  & 34  & 61 \\
\%  & 29 & 58 & 25 & 58  & XX \\
P(lens) & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 \\

\hline
\end{tabular}
\end{center}
{KnCa}-- Known lens candidates \\
{KnCo}-- Known confirmed lenses \\
{NeCa}-- New lens candidates  \\
\end{table}

@@

SW50 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\ 

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
\caption{ \label{fig:lc}
Sample of lens candidates with G$>=$1.3.
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
\caption{ \label{fig:lc1}
Sample of lens candidates G$>=1.3$.
}
\end{center}
\end{figure*}

{\it Describe which lenses were recovered and explain any cases missed by
citizen scientists}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
as a function of the Einstein radius and arc $g$ band magnitudes for
three lens samples, namely, simulated lenses, known confirmed lenses and
the lens candidates sample. XXXX sims are stage1 and real sample values
are for stage 2. }
\end{center}
\end{figure*}

{\it Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
as function of probability P.

Summarize performance at some fiducial threshold: eg P = 95\%.}

\subsection{Image separation distribution}
\label{sec:results:isd}

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
\caption{ \label{fig:isd} Image separation distribution. Comparing
theoretical predictions with the \cfhtls known lens samples (REF) and
the same \cfhtls sample after combining with the incremental lens sample
from \sw }
\end{center}
\end{figure}

{\it Differences with robots: what types of lenses are found at \sw?

Selection function. Missing system.

Describe the importance of this kind of study 
- being able to quantify the completeness of the lens samples
- state how this will be used in a future \sw paper }

\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
\caption{ \label{fig:zlre}
Comparison of Lens redshift and magnitude as a function of Arc radius for all three lens samples,
namely, from \sw, SARCS and those from the RingFinder. Also,
corresponding histograms are shown.}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
\caption{ \label{fig:stackre}
Detections by three methods the Ringfinder, \sw and the Arcfinder as a
function of the Einstein radius and $g$ band magnitude of the lensed
images. XXXX check how different are the estimates from the different measurement techniques for a given lens candidates. }
\end{center}
\end{figure}

{\bf TBD: 
add section on offline analysis - extra lenses found etc;  
expand FP section;  
mention EGS moustakas and other lens samples; 
comment on any lensed quasars, on any exotic lenses;
check if some candidates were detected because they were hidden
underneath the sims ie. from the D11;
}

\subsection{Blind Lens Search}
We looked at the locations of simulated and real lenses from our data
those were missed by \sw compared to the locations of the lenses that
got detected. The real lens sample consists of a total of XXXX candidates
which have $P_l>2.e-5$XXXXX (check this) and received a rank of G$>0$ from the
expert. We do not find any obvious dependency in the rate of detections
as a function of the position of a given lens for both simulated and
real lens sample. Thus, the completeness of the lens sample is not
affected by whether a lens is located close to the border or well within
the center (see  Figure~\ref{fig:comppos}).

\begin{figure*}
\begin{center}
\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
\caption{ \label{fig:comppos}
Completeness as a function of location of lenses. Simulated lenses (left) and
real lens candidate (right) are shown. {\bf: TBD - Add a third color for
P$>$ Pthresh which will be defn of "accepted"} Irrespective of whether the
lenses are detected or rejected and whether they are simulated or real,
there is no obvious dependency on where the lenses are located. 
}
\end{center}
\end{figure*}

\subsection{Limitations and Caveats of the training sample}
The simulated sample has certain limitations due to lack of our understanding of
various phenonmena in the Universe and due to uncertainties in various
parameters of our model. Here, we describe some of the cases or aspects in which the
simulations are known to have failed or seem unrealistic.

The SW lenses are different from the robotically (RingFinder and ArcFinder) detected lenses, in the following ways.
XXXXX

>>>>

Since the inception of the first citizen science project, Galaxy Zoo, to
classify galaxy morphologies \citep{Lintott2008}, several astronomy
and non-astronomy projects have been launched by the Zooniverse leading
to many interesting project. For example, PlanetHunters
has discovered XXX transiting exoplanets \citep{Schwamb2012},
Supernova XXX add ref and XXX add ref

@@

\subsection{Image Presentation in \sw}
\label{sec:data:impres}
%{\it Preparation of data: divide survey into overlapping tiles. Presentation of images. Uniform scales, to build intuition and avoid rescales due to bright objects. Arcsinh stretch, to bring out low SB features. Approximately optimized, how? Examples of images.}

Our aim is to do a blind lens search over the entire \cfhtls
\textsc{wide}. We use the $g$, $r$ and $i$-band color imaging which are
most useful for visual identification of lenses (and provide access to
the $u$ and $z$ band imaging through dashboard with additional tools
XXX).

We make color composite images using publically-available
code\footnote{The open source  color image composition code used in this
work is available from \texttt{http://github.com/drphilmarshall/HumVI}}
following the prescription of \citet{Lupton2004}. Specifically, we first
rescale the pixel values of each channel image into flux units, and
then apply an arcsinh stretch. The stretch parameters are chosen
using a small random sample of images, to ensure that the background
noise is just visible, and that the centres of bright, intermediate
resdhift galaxies are not saturated. The color scales are chosen to
maximize the contrast between faint extended objects. These parameters
are then fixed during the production of all the tiles, in order to
allow straightforward comparison between one image and another, and for
intuition to be built up about the appearance of stars and galaxies
across the survey.

We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) with an
overlapping region of 10\arcsec (54 pixels) between the neighbouring
cutouts resulting into $\sim$ 430 000 cutouts for the entire \cfhtls
\textsc{wide}. The size of the individual cutout is determined by
optimising factors such as the typical angular scales of gravitational
lenses, the number of objects seen in a single cutout and the total
number of image cutouts in the survey. It is possible that a lens
candidate happens to be too close to the edge of a cutout, the overlap
between neighbouring cutout allows the inspector to get a clearer view
of the same candidate in at least one of the cutouts. We note that since
the images are shown randomly, an inspector may not necessarily come
across the neighbouring cutout unless the inspector classifies a large
number of images. This is not a problem since our user base is extremely
large and we receive multiple classifications of the same cutout.

@@

At galaxy-scales, we focus on two primary lens searches. The \rf
\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
of isolated and massive early-type galaxies. By subtracting the PSF-matched
$i$-band images from the $g$-band images, the algorithm looks for excess flux
in the bluer $g$-band. An object detector measures the properties of these
residual blue features, and candidates meeting length-width ratio and
tangential alignment criteria are then visually inspected to form the final
sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
photometrically-classified early type galaxies, or objects selected to have
red centers and blue outer parts, from the T06 CFHTLS data release catalogs. 
14370 were found to show detectable blue residuals, and 2524 were visually
inspected, having passed the automatic feature selection process. This led to
a sample of 42 good quality (\texttt{q\_flag} = 3) and 288 medium quality
(\texttt{q\_flag} = 2) lens candidates. In addition to this well defined
sample, \citet{Gavazzi2014} reported a further 71 serendipitously detected
lens candidates.  From this sample of ``\rf candidates,'' the SL2S team
found, during their follow-up campaign, 39 confirmed lenses (and 17 promising
candidates). We use this sample of 39 ``confirmed \rf lenses'' in our
completeness analysis.

@@

On the other hand, the \af \citet{More2012} was used for
finding blue arc-like features in the complete \cfhtls data withouth any
pre-selection on the type of the lensing object. The search was carried
out in the g-band which is the most efficient wavelength to find typical
lensing galaxies. This sample, called the SARCS, has 55 promising and a
total of 127 lens candidates and consists of both galaxy and
groups/cluster scale lens candidates. Arc finding is better suited for
lensed images or arcs with larger image separations i.e. more massive
systems like groups and clusters. Thus, the SARCS sample has mostly
groups/cluster-scale lenses and a few galaxy-scale lenses.

@@

@@

We use the $L-\sigma$ relation from
\citep{Parker2005} to get the velocity dispersion as given in Eq.~\ref{magstar2}.

@@

Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
Lens shear pa &  0 & 180 & 0 & 180  \\
Source ellipticity & 0.1 & 0.6 & & \\
Source PA & 0 & 180 & & \\
\hline
\end{tabular}
{ $\dagger$} -- corresponds to the factor used for Groups scale lenses. 
\end{center}
\end{table}
\subsubsection{Groups-scale lenses}

@@

@@

We selected a sample of 450 duds for the Stage I classification in \sw
and a sample of 500 false positives for the Stage II
inspection. The sample of false positives was selected from
the candidates which passed the Stage I of \sw. We note that this is the
first time, we have a systematically compiled sample of visually
inspected false positives by the \sw users and categorized by the
science team. Such a sample is tremendously helpful for training and
understanding performances of various lens finding algorithms
\citep{Chan2014}. {\bf TBA data products; make the duds and FP sample available}

\begin{figure}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
\caption{ \label{fig:exp_pn} Comparison of the P(lens) with the expert
grades and number of classification for each subject.  }
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P.pdf}
\caption{ \label{fig:stackP} Total number of detections of the known
candidates, new candidates and the FPs shown relatively for binned
values of P.
}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}
\label{sec:results}

\subsection{\sw Lens Sample}

The \sw works as a single unified neural network which uses the method
of visual inspection to find gravitational lenses. The citizens are
shown images at two stages. At stage I, citizens focus on rapid
inspection and selection of lens candiates ranging from possible lenses
to almost certain lenses. At stage II, citizens carefully inspect the
candidates from stage I and select promising lens candidates only. The
science team consisting of lens experts then categorize and grade the
lens candidates further purifying the sample of lens candidates. In
Table~\ref{tab:stats}, we list the total number of detections of the
known lens candidates, known confirmed lenses and the new lens
candidates at both stages I and II. The known sample corresponds to the
combined Ring Finder and Arc Finder samples. We also show their
fractions with respect to the total number of lens candidates found at
these stages. We note that all the confirmed lenses found at stage I are
also recovered at stage II whereas a small fraction of the known lens
candidates are rejected at stage II. Also, the new lens candidates
increases the known lens candidates sample by over 50\%.

Below, we describe the steps taken after stage II for selecting the
final sample of lens candidates.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsubsection{Selection of the \sw lens candidates}
\label{sec:results:stage1}
The images inspected in \sw are assigned probabilities (P) through the
\sw Analysis Pipeline (SWAP), built in the \sw system (see Paper I).
In an ideal situation, at the end of stage II, all images containing
lenses would have high P values and those without lenses will have low P
values. However, practically, a fraction of the real lenses will be
assigned low P value decreasing the completeness and a fraction of non-lenses
will be assigned high P value decreasing the purity. Our goal is to find
a P value which will result in acceptable levels of completeness and
purity of the final sample of lens candidates.

As this is the first \sw lens search, we explore a large range in the P
value to understand the balance between the real lens candidates and
false positives. In \Fref{fig:exp_pn}, we plot the distribution of
false positives and real lens candidates categorized by the lens experts
as a function of their P value. As expected, the fraction of real lens
candidates is higher for higher P values and it decreases for lower P
values. We note that from P$\sim$0.7 onwards to lower P values, the fraction of
false positives starts to exceed the fraction of real lens candidates.
This could be a good threshold to choose to maximize the purity of the final
sample. However, we choose P$>$0.3 as our threshold to increase the
completeness of our sample. We achieve further purity by including the
grades of the lens experts.

\begin{table}
\begin{center}
\caption{ \label{tab:stats} 
Statistics of detections in \sw }
\begin{tabular}{l l l l l l l}
\hline
   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{4}{c}{Stage II} \\ 
      & KC  &  KL  & KC & KL & NC & AC\\
\hline
\hline
Number  & 128 & 34 & 107  & 34  & 61 & 168\\
\%  & 29 & 58 & 25 & 58  & 12 & 34\\
P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 & 0.3\\

\hline
\end{tabular}
\end{center}
{KC}-- Known lens candidates \\
{KL}-- Known confirmed lenses \\
{NC}-- New lens candidates  \\
{AC}-- All (known and new) lens candidates  \\
P$_{\rm thresh}$ -- systems with P above this threshold are selected \\
Note about \%: For KC and KL, fractions are with respect to the known
population whereas for NC and AC, fractions are with respect to the
total population of lens candidates. \\
\end{table}

@@

All images with P$>$0.3, at the end of stage II, are inspected by three
lens experts (AM, AV, PJM) and are assigned integral grades from 0,1,2
or 3 which imply that the candidate is almost certainly not a lens,
possibly a lens, probably a lens and almost certainly a lens,
respectively. This process led to a final sample of 61 new lens
candidates with averaged grade $\ge$1.3 (see Table~\ref{tab:swcands})
and are shown in \Fref{fig:lc}. For this final sample, we give a \sw ID
and Name of the lens system, Ra, Dec, photometric redshift ($z_{phot}$),
$i$ band magnitude of the lensing galaxy, averaged grade from the lens
experts, zoo ID (identifier used in
TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for
\sw), P value at stage II and a visual categorization of type of lensed
images and the lensing galaxy in the Comments column in
Table~\ref{tab:swcands}. Whenever available the lens properties are
taken from the \cfhtls photometric catalog \citep{Coupon2009} otherwise
the reported lens galaxy positions are measured visually. The visual
categorization of the lens type is only suggestive and the explanation
of the notations in the Comments column is given at the bottom of the
table.

As the first lens search was a blind search with no preselection of
candidates using any algorithm, we expected to find various types of
lenses and this is indeed what we find. The final sample consists of
both galaxy and groups-scale lens candidates. There are detections of
elongated arcs and point-like quasar lensed images. Most of them are
brighter in bluer $g$ band but some candidates brighter in the redder
$i$ band are also found.

{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
and P value comparison, what about the duplicate lenses near the borders
- stats on those?  check the detection plot of arc mag / Reinst and find out why some of
the bins have unexpected results}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
\caption{ \label{fig:lc}
Sample of lens candidates with G$>=$1.3.
}
\end{center}
\end{figure*}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection{Measurements of lens and arc properties}
\label{sec:results:meas}

In the subsequent sections, we make comparison of various properties of
the lens candidates. Here, we describe how we measured those properties,
namely, the lens redshift, the Einstein radii and the total flux of the
arcs.

We use the publicly available redshifts for the lens galaxy from the
\cfhtls photometric catalogs \citep{Coupon2009}. The definition of the
Einstein radius is different in different cases. For the galaxy-scale
lenses in the simulated sample, we use the value of the input lens model
parameter for the $R_{\rm E}$. For groups-scale lenses, since the lens
model is multi-component, we need to determine the $R_{\rm E}$ from the
image positions. We use half of the averaged image separations of the
lensed image counterparts with minimum and maximum image separations.
For the \rf sample, the arcs are detected in the scaled difference image
between $g$ and $i$ bands where the lensing galaxy is subtracted
\citep[for details, see]{Gavazzi2014}. We use the peak position of the
lensed images measured by running {\sc sextractor} on this difference
image and identified visually. We calculate the image separation from
the lens center as an estimate of the $R_{\rm E}$. For the \af (SARCS)
sample, we use the same definition as above except that the peak
position is identified either by the \af or visually. For the \sw lens
sample, the same definition is used where the peak positions are
identified either with \af or {\sc sextractor}.

The total flux of the arc is measured in the $g$ band. For the simulated
sample, we multiply the magnification of the second brightest image with
the source magnitude. For the \rf sample, we use the flux of the lensed
images measured by {\sc sextractor} from the scaled difference image,
that is, $g-\alpha i$ and convert it to the $g$ band flux using mean
colors of the foreground and background population. For the \af and the
\sw sample, we integrate the flux in the image pixels identified by \af
or {\sc sextractor}.

We determine what fraction of the known sample of lenses are recovered by \sw. In
Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the known
candidates and $\sim$~60\% of the known confirmed lenses are found at
stages I and II in \sw. The left and the middle panels of
\Fref{fig:compre} show the fraction of detections as a function of arc
magnitude and the Einstein radius of the lens systems. As expected, we
find that systems with brighter images and/or with larger Einstein radii
are detected more often in \sw.

We find that most of the confirmed lenses and candidates that are missed by \sw
are systems with fainter arcs and smaller Einstein radii and they come
from the \rf sample. The main reason why \rf found such
candidates is because their team used lensing
galaxy-subtracted images to detect the presence of the lensed images
both during the automated object-finding phase and during the visual
inspection and classification of their candidates. This approach
naturally improves the detection efficiency at smaller Einstein radii
and for fainter systems. The \sw volunteers were not shown any
galaxy-subtracted images. However, in light of the improved detection
efficiency, this might be a better strategy to adopt for future lens
searches at galaxy-scales with \sw. In the Discussion \Sref{sec:fn}, we
further explore and discuss why the confirmed lenses may have been
missed in \sw.

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
as a function of the arc magnitude ($g$ band) and the Einstein radius for
three lens samples, namely, simulated lenses, known confirmed lenses and
the lens candidates sample. }
\end{center}
\end{figure*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Image separation distribution}
\label{sec:results:isd}

The distribution of image separations (i.e. twice the Einstein radius)
can be used to probe the average density profile of the lens population
\citep{Oguri2006,More2012}.  However, the lens sample found
by the Arc Finder may have incompleteness as a function of the image
separation. Thus, the lack of understanding of the selection function of
the lens sample may affect the constraints on the density profile.  A
blind lens search done by visual inspection alone e.g. by \sw may find
lenses missed by the Arc Finder search and thereby, improve
completeness. Furthermore, the completeness of the lens sample found by \sw is
characterised with the help of the simulated sample. For example, in the
right most panel of \Fref{fig:compre}, we plot the completeness of the
simulated sample found at stage I of \sw as a function of the arc
magnitude and Einstein radius. We find that the sample is more than 80\%
complete between image separations 2"-10".

In \Fref{fig:isd}, we plot theoretical curves for the image
separationd distribution corresponding to three density profiles,
namely, isothermal sphere (IS), NFW \citep{Navarro1997} and Total profile which has
NFW and Hernquist profiles combined with an adiabatically contracting model for
dark matter component \citep{Gnedin2004} taken from \citet{More2012}.

Finding gravitational lenses is a difficult and complex task. No one
method is perfect. Each method has some advantages over the other. It
may be the case that a single method may not be the best means for
optimising completeness and purity. Visual inspection will likely be
required for pruning candidates at some stage of lens candidate
selection even in the future. Therefore, we would like to understand how
best we should combine the strengths of robots and humans to optimize
the lens finding method.

In this section, we attempt to understand and compare the lens
(candidates) that are found by the lens finding robots and missed by humans
and vice versa.

\subsection{False negatives: known lenses missed by \sw}
\label{sec:fn}
Like any lens finding method, the \sw system can fail to detect
certain kinds of lenses. We explore and discuss why some of the known
confirmed lenses may have been missed. About 40\% of the known confirmed sample of
lenses are missed (see \Tref{tab:stats}). And, XXXX

Among the confirmed lenses from the \rf, about 50\% are missed. Out of
the missed sample of 18 lenses, about half of them are visually
difficult to detect and the other half seem to show faint blue smudges
around galaxies which should have been easier to identify.  {\bf Let us
compare the two samples to see if there are any obvious differences.
only 2 out of this sample of 18 were detected at stage I (reached high P
even with fewer classifications) and missed at stage II (P value was low
even after recieving very many classifications). The rest of the 16
lenses were rejected right at stage I XXX}

If we consider the \af lenses, only 6 out of the 26 ($\sim$23\%) were
missed by \sw. One of those 6 lenses was detected at stage I but failed
to get high enough P value at stage II even after receiving a total of
50 classifications (set as the upper limit). The rest of the 5 lenses
are already rejected at stage I. Upon visual inspection of these 5
systems, they appear to be difficult to identify as lenses because
either the lensed images are faint, have low curvature, are close to the
edge and/or are not visible due to proximity to an extremely bright
galaxy ({\bf show some examples XXX}).

\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
\caption{ \label{fig:zlre}
Comparison of the lens redshift and of the arc magnitude with the
Einstein radius for all of the three lens samples, namely, from the \rf (green dots),
\sw (all candidates black circles and new candidates only in blue dots)
and \af (red dots). }
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
\caption{ \label{fig:stackre}
Candidate detections by the \rf, \sw and the \af as a
function of the Einstein radius and $g$ band magnitude of the lensed
images. (XXXX check how different are the estimates from the different
measurement techniques for a given lens candidates.) }
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
\caption{ \label{fig:isd} Image separation distribution. Comparing
theoretical predictions (solid curves) with the \cfhtls known lens
samples (REF , green points) and the same \cfhtls sample after combining
with the incremental lens sample from \sw (magenta points). The \sw only
sample including new and known lens candidates are shown with blue
points. }
\end{center}
\end{figure}

Efficiency of a visual search can vary in different sections of an
image. Our eyes tend to focus usually at the center of an image and lens
candidates close to the borders could go undetected. Therefore, it is
essential to test and understand if \sw tends to miss certain lenses
because they happen to be close to the borders of the image cutouts.

From the SWAP, the image cutouts inspected by the \sw volunteers receive
a status of detected (if P$>$P$_{\rm acc_thresh}$), rejected (if
P$<$P$_{\rm rej_thresh}$) and undecided (if P$_{\rm rej_thresh}$ $<$ P
$<$ P$_{\rm acc_thresh}$). In \Fref{fig:comppos}, we compare the
positions of simulated lenses which are detected (red), undecided
(green) and rejected (blue). We also make the same comparison for the
known lens candidates in the right panel.  We note that for some cases
randomly selected subsamples are shown for the ease of visual
comparison. For example, the absolute number of simulated lenses
detected is too high compared to the rejected sample. We do not find any
strong visual correlation in the rate of detections as a function of the
position for both the simulated and the known lens sample. Thus, the
completeness of the lens sample does not seem to be significantly
affected by whether a lens is located close to the border or well within
the center.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Why \sw candidates were missed by lens finding robots?}

The new lens candidates discovered by \sw are run through the \rf to
trace and understand at what stage the algorithm failed to detect them.

At the first step of the \rf algorithm, a galaxy catalog is generated
based on magnitude, redshift and SED type \citep[see]{Gavazzi2014} to
select galaxies which are most likely to act as lenses. We find that
about 40\% of the new \sw candidates fail to meet this initial selection
criteria e.g. SW1, SW13, SW19, SW22, SW27 and SW30.  All of the lensing
galaxies are bright enough to satisfy the $i<22$ criterion. However,
some of them have a bright companion galaxy, some of them do not look
like E/S0 type galaxies and some are edge on galaxies. {\bf there are a
few which look regular galaxies so which criteria are they failing??}

%% 13 are under mask so no photoz, 10 have photoz (z>0.2 except for 1).

In the following steps, the flux from the galaxy is subtracted from the
scaled difference image to enhance the visibility of the faint blue
lensed features. An object finder is run on this image to quantify the
lensed image properties. About 50\% of the \sw candidates could not be
detected by the object finder because properties such as the image area,
axis ratio, magnitude/color and alignment with respect to the lensing
galaxy are not satisfied. Some of the candidates missed at this stage
are e.g. SW4, SW5, SW6, SW26, SW36, SW39 and SW47.

%% 23/61 miss first step, 30/61 miss auto, 5 pass auto but have poor
%grade from visual classf.

Next, we rerun the \af on the same \sw sample of new candidates. The \af
is directly run an image to look for elongated arc like objects and does
not require a list of targets to begin with. Objects are identified by
placing thresholds on the noise level in the images. Thus, \af
detections are sensitive to changes in the noise levels. Also, the size
of the PSF is important to know what dimensions should be expected for
the arc candidates.

Originally, the \af was run on a large image with an area of $\sim 19400
\times 19400$ pixels$^2$. For the rerun, we work with much smaller
images because this is faster but this affects the number and type of
arc detections. We find that about 30\% of the new candidates are detected
without changing any of the thresholds in the code because of the change
in the noise level.

{\bf TBD: 
comment on any lensed quasars, on any exotic lenses;
of course, there must be lenses which cannot be detected currently by
either robots/humans
check if some candidates were detected because they were hidden
underneath the sims ie. from the D11;
}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Limitations and Caveats of the training sample}

The simulated sample is not perfect because our understanding of various
phenomena in the Universe is not complete and because of the uncertainties in
the parameters of our model. Here, we describe some of the cases or
aspects in which the simulations are known to have failed or seem
unrealistic.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
\caption{ \label{fig:comppos}
Completeness as a function of position of lens systems. Simulated lenses
(left) and real lens candidates (right) are shown. Irrespective of the
status of the lenses, that is, detected, undecided or rejected, there is
no strong dependency on where the lenses are located both for the
simulated and the real sample of lens candidates. }
\end{center}
\end{figure*}

The SW lenses are different from the robotically (\rf and \af) detected lenses, in the following ways.
XXXXX

@@

SW40 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\ 

@@
